### 2015-05-26 graphs/ipsec-ftp-bench.tex
raw results

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {FTP transfer insed IPSec tunnel},
        width  = 0.95*\textwidth,
        height = 8cm,
        major x tick style = transparent,
        ybar=10pt,
        bar width=8pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0, ymax=12,
        symbolic x coords={oot, none:none, aes256cbc:none, aes256cbc:sha256, aes256gcm},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.1,
    ]

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {FTP transfer inside an IPSec tunnel},
        width  = 0.95*\textwidth,
        height = 8cm,
        major x tick style = transparent,
        ybar=10pt,
        bar width=8pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0, ymax=12,
        symbolic x coords={oot, none:none, aes256cbc:none, aes256cbc:sha256, aes256gcm},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.1,
    ]

### 2015-05-26 graphs/openvpn-tls-bench.tex
raw results

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {TLS connections through OpenVPN},
        width  = 0.7*\textwidth,
        height = 8cm,
        major x tick style = transparent,
        ybar=10pt,
        bar width=8pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0,
        symbolic x coords={RSA-1024, RSA-2048, RSA-4096},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.1,
    ]

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {TLS connections through OpenVPN},
        width  = 0.7*\textwidth,
        height = 8cm,
        major x tick style = transparent,
        ybar=10pt,
        bar width=8pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Connections per minute},
        xlabel = {},
        ymin=0,
        symbolic x coords={RSA-1024, RSA-2048, RSA-4096},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.1,
    ]

### 2015-05-26 implementation.tex
raw results

\noindent The first liberty is a laste\footnote{A vulnerability note as been issued by Carnegie Mellon University Computer Emergency Response Team in early 2009 (last revision)~\cite{CERT2009}, in response to a research of University of London~\cite{Albrecht:2009} presenting a plaintext-recovering attack against SSH when CBC mode is used, but the OpenSSH update took only place in october 2014.}.
Even if it is not recommended, the user can still enable this mode by explicitly configuring it in the \texttt{sshd\_config} options.

>>>>

\noindent The first liberty is a response to an old vulnarability\footnote{A vulnerability note as been issued by Carnegie Mellon University Computer Emergency Response Team in early 2009 (last revision)~\cite{CERT2009}, in response to a research of University of London~\cite{Albrecht:2009} presenting a plaintext-recovering attack against SSH when CBC mode is used, but the OpenSSH update took only place in october 2014.}.
Even if it is not recommended, the user can still enable this mode by explicitly configuring it in the \texttt{sshd\_config} options.

### 2015-05-26 results.tex
raw results

\subsection{OpenVPN}
The figure~\ref{fig:ping-benchmark-openvpn} shows the results for different payload sizes.

@@

@@

\subsection{IPsec}
The figure~\ref{fig:ping-benchmark-ipsec} studies the same payload size as OpenVPN, but with an extra experimental hardware implementation of AES mode GCM.

@@

@@

\subsection{OpenSSH}
The figure~\ref{fig:openssh-bench} shows the results for a file transfer over an SSH tunnel.
For this application, there is no none:none couple case inside the tunnel, as it would be the same as a transfer outside the tunnel.

\begin{figure}[ht]
\input{graphs/openssh-bench}
\caption{File transfer over an SSH tunnel.}{The background stripped bars are the CPU usage.}
\label{fig:openssh-bench}
\end{figure}

@@

\subsection{OpenVPN}
The figure~\ref{fig:openvpn-ftp-bench} shows the performance of the file transfer over an OpenVPN tunnel.

\begin{figure}[ht]
\input{graphs/openvpn-ftp-bench}
\caption{FTP file transfer over an OpenVPN tunnel.}{The results inside the tunnel with no encryption nor authentication highlights the overhead OpenVPN adds to the transfer. From there, the throughput only change by a small extent. The poor hardware results also shows the heaviness of OpenVPN on hardware offloading. The background stripped bars are the CPU usage.}
\label{fig:openvpn-ftp-bench}
\end{figure}

@@

\subsection{IPsec}
The figure~\ref{fig:ipsec-ftp-bench} gathers the results of the file transfer over the IPsec tunnel.
\begin{figure}[ht]
\input{graphs/ipsec-ftp-bench}
\caption{FTP file transfer over an IPsec tunnel.}{The advantage of the hardware is a lower CPU usage, at the cost of a few percents lower throughput. The GCM mode is also tested to discuss its implementation in hardware. The background stripped bars are the CPU usage.}
\label{fig:ipsec-ftp-bench}
\end{figure}

>>>>

\subsection{OpenVPN}
The figure~\ref{fig:ping-benchmark-openvpn} shows the results for different payload sizes, which raw results are presented in table~\ref{tab:ping-benchmark-openvpn}

@@

\begin{table}[ht]
\center
\small
\begin{tabular}{l|c|c|c|c|} \cline{2-5}
 & 56B & 1000B & 8000B & 16000B \\ \hline
\multicolumn{1}{|l|}{raw} & 1.444 & 1.929 & 2.811 & 4.322 \\ \hline
\multicolumn{1}{|l|}{none-none} & 2.066 & 2.561 & 4.293 & 6.117 \\ \hline
\multicolumn{1}{|l|}{soft-cbc256-none} &  &  &  & \\ \hline
\multicolumn{1}{|l|}{ba411e-cbc256-none} &  &  &  & \\ \hline
\multicolumn{1}{|l|}{soft-cbc256-sha256} & 2.415 & 3.061 & 5.997 & 9.135 \\ \hline
\multicolumn{1}{|l|}{ba411e-cbc256-sha256} & 2.416 & 3.052 & 5.963 & 9.207 \\ \hline
\end{tabular}
\caption{OpenVN: ping average response time}{the latency is given in milliseconds.}
\label{tab:ping-benchmark-openvpn}
\end{table}

@@

\subsection{IPsec}
The figure~\ref{fig:ping-benchmark-ipsec} studies the same payload size as OpenVPN, but with an extra experimental hardware implementation of AES mode GCM. The raw results are in table~\ref{tab:ping-benchmark-ipsec}.

@@

\begin{table}[ht]
\center
\small
\begin{tabular}{l|c|c|c|c|} \cline{2-5}
 & 56B & 1000B & 8000B & 16000B \\ \hline
\multicolumn{1}{|l|}{raw} & 1.444 & 1.929 & 2.811 & 4.322 \\ \hline
\multicolumn{1}{|l|}{none-none} & 1.545 & 2.045 & 2.997 & 4.703 \\ \hline
\multicolumn{1}{|l|}{soft-cbc256-none} &  &  &  &  \\ \hline
\multicolumn{1}{|l|}{ba411e-cbc256-none} &  &  &  &  \\ \hline
\multicolumn{1}{|l|}{soft-cbc256-sha256} & 1.645 & 2.322 & 4.762 & 7.975 \\ \hline
\multicolumn{1}{|l|}{ba411e-cbc256-sha256} & 1.635 & 2.246 & 4.170 & 6.929 \\ \hline
\multicolumn{1}{|l|}{soft-gcm256} & 1.651 & 2.388 & 5.383 & 9.241 \\ \hline
\multicolumn{1}{|l|}{ba411e-gcm256} & 1.764 & 2.286 & -- & --  \\ \hline
\end{tabular}
\caption{IPsec: ping average response time}{the latency is given in milliseconds. Some results for the GCM mode in hardware are non-existant.}
\label{tab:ping-benchmark-ipsec}
\end{table}

@@

\subsection{OpenSSH}
The figure~\ref{fig:openssh-bench} shows the results for a file transfer over an SSH tunnel.
For this application, there is no none:none couple case inside the tunnel, as it would be the same as a transfer outside the tunnel.
The raw results are gathered in table~\ref{tab:openssh-bench}.

\begin{figure}[ht]
\input{graphs/openssh-bench}
\caption{File transfer over an SSH tunnel}{The background stripped bars are the CPU usage.}
\label{fig:openssh-bench}
\end{figure}

\begin{table}[ht]
\center
\small
\begin{tabular}{l|c|c|c|c|c|c|} \cline{2-7}
 & \multicolumn{2}{c|}{none:none} & \multicolumn{2}{c|}{aes256cbc:none} & \multicolumn{2}{c|}{aes256cbc:sha256} \\ \cline{2-7}
 & Tp.  & CPU & Tp.  & CPU & Tp.  & CPU \\ \hline
\multicolumn{1}{|c|}{Out-of-tunnel} & 11.39 & 7.16 & -- & -- & -- &  -- \\ \hline
\multicolumn{1}{|c|}{Software} & -- & -- & 10.89 & 96.26 & 8.19 &  89.29 \\ \hline
\multicolumn{1}{|c|}{BA414E} & -- & -- & 10.67 & 46.01 & 10.39 & 68.19 \\ \hline
\end{tabular}
\caption{File transfer over an SSH tunnel}{The throughput is in MB/s.}
\label{tab:openssh-bench}
\end{table}

@@

\subsection{OpenVPN}
The figure~\ref{fig:openvpn-ftp-bench} shows the performance of the file transfer over an OpenVPN tunnel.
The data is gathered in table~\ref{tab:openvpn-ftp-bench}.

\begin{figure}[ht]
\input{graphs/openvpn-ftp-bench}
\caption{FTP file transfer over an OpenVPN tunnel}{The results inside the tunnel with no encryption nor authentication highlights the overhead OpenVPN adds to the transfer. From there, the throughput only change by a small extent. The poor hardware results also shows the heaviness of OpenVPN on hardware offloading. The background stripped bars are the CPU usage.}
\label{fig:openvpn-ftp-bench}
\end{figure}

\begin{table}[ht]
\center
\small
\begin{tabular}{l|c|c|c|c|c|c|} \cline{2-7}
 & \multicolumn{2}{c|}{none:none} & \multicolumn{2}{c|}{aes256cbc:none} & \multicolumn{2}{c|}{aes256cbc:sha256} \\ \cline{2-7}
 & Tp.  & CPU & Tp.  & CPU & Tp.  & CPU \\ \hline
\multicolumn{1}{|c|}{Out-of-tunnel} & 11.39 & 7.16 & -- & -- & -- & -- \\ \hline
\multicolumn{1}{|c|}{Inside tunnel} & 5.18 & 42.60 & -- & -- & -- & -- \\ \hline
\multicolumn{1}{|c|}{Software} & -- & -- & 4.78 & 76.60 & 3.87 & 76.03 \\ \hline
\multicolumn{1}{|c|}{BA414E} & -- & -- & 3.35 & 83.74 & 2.84 & 80.89 \\ \hline
\end{tabular}
\caption{FTP file transfer over an OpenVPN tunnel}{The throughput is in MB/s.}
\label{tab:openvpn-ftp-bench}
\end{table}

@@

\subsection{IPsec}
The figure~\ref{fig:ipsec-ftp-bench} gathers the results of the file transfer over the IPsec tunnel.
\begin{figure}[ht]
\input{graphs/ipsec-ftp-bench}
\caption{FTP file transfer over an IPsec tunnel}{The advantage of the hardware is a lower CPU usage, at the cost of a few percents lower throughput. The GCM mode is also tested to discuss its implementation in hardware. The background stripped bars are the CPU usage.}
\label{fig:ipsec-ftp-bench}
\end{figure}

\begin{table}[ht]
\center
\small
\begin{tabular}{l|c|c|c|c|c|c|c|c|} \cline{2-9}
 & \multicolumn{2}{c|}{none:none} & \multicolumn{2}{c|}{aes256cbc:none} & \multicolumn{2}{c|}{aes256cbc:sha256} & \multicolumn{2}{c|}{aes256gcm} \\ \cline{2-9}
 & Tp.  & CPU & Tp.  & CPU & Tp.  & CPU & Tp.  & CPU \\ \hline
\multicolumn{1}{|c|}{Out-of-tunnel} & 11.39 & 7.16 & -- & -- & -- & -- & -- & -- \\ \hline
\multicolumn{1}{|c|}{Inside tunnel} & 10.21 & 14.68 & -- & -- & -- & -- & -- & -- \\ \hline
\multicolumn{1}{|c|}{Software} & -- & -- & 8.83 & 63.74 & 6.47 & 74.64 & 5.09 & 89.66 \\ \hline
\multicolumn{1}{|c|}{BA414E} & -- & -- & 8.52 & 14.87 & 5.80 & 17.25 & -- & -- \\ \hline
\end{tabular}
\caption{FTP file transfer over an IPsec tunnel}{The throughput is in MB/s.}
\label{tab:ipsec-ftp-bench}
\end{table}
